Paper changepoint

### 2019-01-14 paper-comparison/paper_changepoint.Rmd
Begin LDA comparison and fix model stash path
start to compare ldas with adjusted/nonadjusted data
store model objects in dropbox

#### Load LDA ####
load('/Users/renatadiaz/Documents/model-stash/ldats_lda.Rds')

@@

# # run models with 1, 2, 3, 4, 5 changepoints
# cp_results_rodent = changepoint_model(ldats_lda_selected[[1]], x, 1, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda1.Rds')
# rm(cp_results_rodent)
# 
# cp_results_rodent2 = changepoint_model(ldats_lda_selected[[1]], x, 2, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent2, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda2.Rds')
# rm(cp_results_rodent2)
# 
# cp_results_rodent3 = changepoint_model(ldats_lda_selected[[1]], x, 3, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent3, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda3.Rds')
# rm(cp_results_rodent3)
# 
# cp_results_rodent4 = changepoint_model(ldats_lda_selected[[1]], x, 4, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent4, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda4.Rds')
# rm(cp_results_rodent4)
# 
# cp_results_rodent5 = changepoint_model(ldats_lda_selected[[1]], x, 5, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent5, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda5.Rds')
# rm(cp_results_rodent5)
# 
# cp_results_rodent6 = changepoint_model(ldats_lda_selected[[1]], x, 6, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent6, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda6.Rds')
# rm(cp_results_rodent6)
#

#### Changepoint model selection ####
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda1.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda2.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda3.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda4.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda5.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda6.Rds')

@@

#### Load LDA ####
load('/Users/renatadiaz/Documents/model-stash/paper_lda.Rds')

@@

# # run models with 1, 2, 3, 4, 5 changepoints
# cp_results_rodent = changepoint_model(ldamodel, x, 1, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda1.Rds')
# rm(cp_results_rodent)
# 
# 
# cp_results_rodent2 = changepoint_model(ldamodel, x, 2, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent2, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda2.Rds')
# rm(cp_results_rodent2)
# 
# cp_results_rodent3 = changepoint_model(ldamodel, x, 3, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent3, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda3.Rds')
# rm(cp_results_rodent3)
# 
# cp_results_rodent4 = changepoint_model(ldamodel, x, 4, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent4, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda4.Rds')
# rm(cp_results_rodent4)
# 
# cp_results_rodent5 = changepoint_model(ldamodel, x, 5, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent5, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda5.Rds')
# rm(cp_results_rodent5)
# 
# cp_results_rodent6 = changepoint_model(ldamodel, x, 6, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent6, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda6.Rds')
# rm(cp_results_rodent6)

## ----paper paper selection-----------------------------------------------
ntopics = ldamodel@k
# Load models and compare deviance to select the best one
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda1.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda2.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda3.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda4.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda5.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda6.Rds')

>>>>

#### Load LDA ####
load('~/Dropbox/ldats-models/ldats_lda.Rds')

@@

# # run models with 1, 2, 3, 4, 5 changepoints
# cp_results_rodent = changepoint_model(ldats_lda_selected[[1]], x, 1, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent, file = '~/Dropbox/ldats-models/paper_cpt_ldats_lda1.Rds')
# rm(cp_results_rodent)
# 
# cp_results_rodent2 = changepoint_model(ldats_lda_selected[[1]], x, 2, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent2, file = '~/Dropbox/ldats-models/paper_cpt_ldats_lda2.Rds')
# rm(cp_results_rodent2)
# 
# cp_results_rodent3 = changepoint_model(ldats_lda_selected[[1]], x, 3, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent3, file = '~/Dropbox/ldats-models/paper_cpt_ldats_lda3.Rds')
# rm(cp_results_rodent3)
# 
# cp_results_rodent4 = changepoint_model(ldats_lda_selected[[1]], x, 4, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent4, file = '~/Dropbox/ldats-models/paper_cpt_ldats_lda4.Rds')
# rm(cp_results_rodent4)
# 
# cp_results_rodent5 = changepoint_model(ldats_lda_selected[[1]], x, 5, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent5, file = '~/Dropbox/ldats-models/paper_cpt_ldats_lda5.Rds')
# rm(cp_results_rodent5)
# 
# cp_results_rodent6 = changepoint_model(ldats_lda_selected[[1]], x, 6, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent6, file = '~/Dropbox/ldats-models/paper_cpt_ldats_lda6.Rds')
# rm(cp_results_rodent6)
#

#### Changepoint model selection ####
load('~/Dropbox/ldats-models/paper_cpt_ldats_lda1.Rds')
load('~/Dropbox/ldats-models/paper_cpt_ldats_lda2.Rds')
load('~/Dropbox/ldats-models/paper_cpt_ldats_lda3.Rds')
load('~/Dropbox/ldats-models/paper_cpt_ldats_lda4.Rds')
load('~/Dropbox/ldats-models/paper_cpt_ldats_lda5.Rds')
load('~/Dropbox/ldats-models/paper_cpt_ldats_lda6.Rds')

@@

#### Load LDA ####
load('~/Dropbox/ldats-models/paper_lda.Rds')

@@

# # run models with 1, 2, 3, 4, 5 changepoints
# cp_results_rodent = changepoint_model(ldamodel, x, 1, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent, file = '~/Dropbox/ldats-models/paper_cpt_paper_lda1.Rds')
# rm(cp_results_rodent)
# 
# 
# cp_results_rodent2 = changepoint_model(ldamodel, x, 2, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent2, file = '~/Dropbox/ldats-models/paper_cpt_paper_lda2.Rds')
# rm(cp_results_rodent2)
# 
# cp_results_rodent3 = changepoint_model(ldamodel, x, 3, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent3, file = '~/Dropbox/ldats-models/paper_cpt_paper_lda3.Rds')
# rm(cp_results_rodent3)
# 
# cp_results_rodent4 = changepoint_model(ldamodel, x, 4, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent4, file = '~/Dropbox/ldats-models/paper_cpt_paper_lda4.Rds')
# rm(cp_results_rodent4)
# 
# cp_results_rodent5 = changepoint_model(ldamodel, x, 5, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent5, file = '~/Dropbox/ldats-models/paper_cpt_paper_lda5.Rds')
# rm(cp_results_rodent5)
# 
# cp_results_rodent6 = changepoint_model(ldamodel, x, 6, weights = rep(1,length(year_continuous)))
# save(cp_results_rodent6, file = '~/Dropbox/ldats-models/paper_cpt_paper_lda6.Rds')
# rm(cp_results_rodent6)

## ----paper paper selection-----------------------------------------------
ntopics = ldamodel@k
# Load models and compare deviance to select the best one
load('~/Dropbox/ldats-models/paper_cpt_paper_lda1.Rds')
load('~/Dropbox/ldats-models/paper_cpt_paper_lda2.Rds')
load('~/Dropbox/ldats-models/paper_cpt_paper_lda3.Rds')
load('~/Dropbox/ldats-models/paper_cpt_paper_lda4.Rds')
load('~/Dropbox/ldats-models/paper_cpt_paper_lda5.Rds')
load('~/Dropbox/ldats-models/paper_cpt_paper_lda6.Rds')
